 

### 2021-07-28 index.Rmd
mayor update repo
- se elimina docs
- paper pasa a estar en el root
- prep data y analysis se mantienen en production

---
author: " "
bibliography:
- '../input/bib/zlibrary.bib'
csl:
- '../input/bib/apa6.csl'
title: " "
output:
    bookdown::html_document2:
        smart: false
        includes:
          in_header: head_github-activity.html
---

@@

### This is the project website for the paper "Economic inequality and its influence on the justification of legitimate income differences. {.left}

@@

### Authors:

- Julio Iturra, Centro de Estudios de Conflicto y Cohesión Social - COES [julioiturra@uchile.cl](julioiturra@uchile.cl)
- Juan Carlos Castillo, Departamento de Sociología, Universidad de Chile.
- Catalina Rufs, Pontificia Universidad Católica de Chile.

@@

### Structure of the project website:

@@

### Reproducibility and documentation

>>>>

---
author: " "
bibliography:
- 'input/bib/zlibrary.bib'
csl:
- 'input/bib/apa6.csl'
title: " "
output:
    bookdown::html_document2:
        smart: false
        includes:
          in_header: "input/head_github-activity.html"
---

@@

# This is the project website for the paper "Economic inequality and its influence on the justification of legitimate income differences. {.left}

@@

# Authors:

- Julio Iturra, Centro de Estudios de Conflicto y Cohesión Social - COES [julioiturra@uchile.cl](julioiturra@uchile.cl)
- Juan Carlos Castillo, Departamento de Sociología, Universidad de Chile.
- Catalina Rufs, Pontificia Universidad Católica de Chile.
- Luis Maldonado, Instituto de Sociología, Pontificia Universidad Católica de Chile.

@@

# Structure of the project website:

@@

## Reproducibility and documentation
